MA_Results

### 2022-07-25 Markdown/Manuscript/Child_RMDs/MS_Aims.Rmd
fiddling

<!-- Add aims text here -->
We have consolidated and refined these and other recommended guidelines for OSHEMs as part of a framework for developing an open source model of youth mental health. In this paper, we describe our motivation for developing the framework, the rationale for each included standard, the software toolkits we have developed to help meet each standard and a worked example of a modelling project developed using this framework.

>>>>

<!-- Add aims text here -->
In this paper, we describe:

- a proposed set of guidelines for implementing OSHEMS;
- a framework for applying these guidelines to the development of a reference OSHEM in youth mental health; 
- a worked example of a modelling project developed with the framework.

<!-- We are currently developing **readyforwhatsnext**, a reference OSHEM that aims to examine multiple potential population level strategies for promoting mental wellbeing and preventing and treating mental disorders in young people. -->
<!-- We have consolidated and refined these and other recommended guidelines for OSHEMs as part of a framework for developing an open source model of youth mental health.  -->

### 2022-07-25 Markdown/Manuscript/Child_RMDs/MS_Imp_Guidelines.Rmd
fiddling

Adherence to explicit guidelines is an essential requirement for modelling in healthcare [@Erdemir2020]. Guidance for implementing OSHEMs remains scarce and piecemeal and needs to be improved [@Sampson2019].  Guidelines on health economic model transparency were published ten years ago [@Eddy2012] and made recommendations on documenting models; however, notably missing were recommendations on the sharing of model code and data. More recent and more general modelling guidance [@Erdemir2020] recommends the sharing of code and data through digital repository services <!-- such as GitHub [@github2007] and Zenodo [@Zenodo2013] --> and the use of version control systems <!-- such as Git [@git20XX].  -->

Based on existing open science guidance and our own experience, we have identified 20 guidelines for implementations of OSHEMs that are **TIMELY**:

 - **Transparent**: people can easily see how a model has been implemented and tested;
 - **Iterative**: a model is routinely updated to maintain and improve validity;
 - **Modular**: models and their components can be combined to extend their scope;
 - **Epitomising**: a model code is sufficiently general to be be re-used in multiple decision contexts;
 - **Licensed**: a model, its components and derivatives are persistently re-usable by other modellers; and
 - **Yielding**: a model can be simply, flexibly and reliably used as a decision aid.

>>>>

Guidelines on health economic model transparency were published ten years ago [@Eddy2012] and made recommendations on documenting models; however, notably missing were recommendations on the sharing of model code and data. More recent and more general modelling guidance [@Erdemir2020] recommends the sharing of code and data through digital repository services <!-- such as GitHub [@github2007] and Zenodo [@Zenodo2013] --> and the use of version control systems. <!-- such as Git [@git20XX].  --> Based on these and other existing sources of guidance and our own experience, we propose 20 guidelines for implementing OSHEMs that are **TIMELY**:

 - **Transparent**: people can easily see how a model has been implemented and tested;
 - **Iterative**: a model is routinely updated to maintain and improve validity;
 - **Modular**: models and their components can be combined to extend their scope;
 - **Epitomising**: model code is sufficiently general to be be re-used in multiple decision contexts;
 - **Licensed**: a model, its components and derivatives are persistently re-usable by other modellers; and
 - **Yielding**: a model can be simply, flexibly and reliably used as a decision aid.

### 2022-07-25 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
fiddling

<!-- `r ifelse(is.na(params$X@background_1L_chr),"",params$X@background_1L_chr)`  -->
Computational models have become essential tools for health policy development [@dakin2015influence; @Erdemir2020]. Although influential and widely used, these models routinely contain errors [@Radeva2020], are rarely adequately validated [@Ghabri2019], can be difficult to reproduce [@Jalali2021; @McManus2019; @Bermejo2017] and are likely to be infrequently updated or revised [@Sampson2017]. To help address these issues, there is growing support for greater use of open source health economic models (OSHEMs) that grant liberal permissions to access and re-use model source code and data [@Pouwels2022].

Enabling multiple modelling teams to collaboratively re-use, test and extend one another's work can make complex modelling projects more tractable [@Arnold2010]. Recommendations to update and refine health economic models as new evidence emerges and decision contexts change [@Jenkins2021], adopt systems modelling approaches for public health economics topics [@SQUIRES2016588] and to develop multiple-application or reference models for re-use by different modelling teams [@Afzali2013] all involve resourcing and quality assurance challenges. For example, complex models may be more prone to error [@Saltelli2019] and reference models require greater investments in model transparency and validation [@Eddy2012; @Feenstra2022].

Open source approaches have been recommended to help develop a mental health modelling field that rarely explores complex dynamic systems [@RN73]. Mental health economic studies predominantly examine the affordability and value for money of individual programs [@RN34]. Yet single purpose models that assume static systems may be inadequate for the decision support needs of policymakers and service planners [@PC2020; @Occhipinti2021]. 
<!-- and for mental health specifically [@Occhipinti2021],  -->
<!-- could provide greater insight about inter-dependencies between candidate policies and the dynamic nature of the mental health systems planning context. Dynamic systems methods might provide the foundations for developing   -->
<!-- and models designed for multiple purposes r -->

Despite the potential benefits, actual implementations of OSHEMs are rare [@Emerson2019; @Michalczyk2018; @Feenstra2022]. Currently there is only one mental health related model (in Alcohol Use Disorder [@Basu2018]) that is indexed in the Open Source Models Clearinghouse [@OSMC_20xx;@Emerson2019]. Other than our own work, we are aware of just one open source mental health reference model - in Major Depressive Disorder - that is currently in development [@IVIMDD2022]. Barriers to adoption of OSHEMs include concerns about intellectual property, confidentiality, model misuse and the resources required to support open source implementations [@Pouwels2022; @Wu2019]. As many health economic models are owned by pharmaceutical companies and consultancies, commercial considerations may also limit the uptake of OSHEMs [@Feenstra2022].

>>>>

<!-- `r ifelse(is.na(params$X@background_1L_chr),"",params$X@background_1L_chr)`  -->
Computational models have become essential tools for health policy development [@dakin2015influence; @Erdemir2020]. Although influential and widely used, these models routinely contain errors [@Radeva2020], are rarely adequately validated [@Ghabri2019] and can be difficult to reproduce [@Jalali2021; @McManus2019; @Bermejo2017]. To help address these issues, there is support for greater use of open source health economic models (OSHEMs) that grant liberal permissions to access and re-use model source code and data [@Pouwels2022].

Complex modelling projects may be more tractable when multiple modelling teams re-use, test and extend one another's work [@Arnold2010]. OSHEMSs might therefore mitigate some barriers to improving the longevity, quality and impact of health economic models.  For example,  health economic models should be updated and refined as new evidence emerges and decision contexts change [@Jenkins2021], but this occurs infrequently [@Sampson2017]. Reference models that can be re-used in multiple health economic modelling projects have been advocated for [@Afzali2013] but require greater investments in model transparency and validation [@Eddy2012; @Feenstra2022]. 
<!-- Systems modelling approaches have been recommended for public health economics topics [@SQUIRES2016588] but complex models may be more prone to error [@Saltelli2019].  -->

<!-- and for mental health specifically [@Occhipinti2021],  -->
<!-- could provide greater insight about inter-dependencies between candidate policies and the dynamic nature of the mental health systems planning context. Dynamic systems methods might provide the foundations for developing   -->
<!-- and models designed for multiple purposes r -->

Despite the potential benefits of OSHEMs, actual implementations  are rare [@Emerson2019; @Michalczyk2018; @Feenstra2022]. Barriers to adoption of OSHEMs include concerns about intellectual property, confidentiality, model misuse and the resources required to support open source implementations [@Pouwels2022; @Wu2019]. As many health economic models are owned by pharmaceutical companies and consultancies, commercial considerations may also limit the uptake of OSHEMs [@Feenstra2022]. Adherence to good practice guidance is an essential requirement for healthcare modelling [@Erdemir2020], but guidelines for implementing OSHEMs remain scarce, piecemeal and need improving [@Sampson2019].

<!-- Open source approaches have been recommended to help develop the mental health modelling field <!-- that rarely explores complex dynamic systems  -->
<!-- [@RN73] but only one mental health related model (in Alcohol Use Disorder [@Basu2018]) is indexed in the Open Source Models Clearinghouse [@OSMC_20xx;@Emerson2019]. Other than our own work, we are aware of just one open source mental health reference model - in Major Depressive Disorder - that is currently in development [@IVIMDD2022]. -->

<!-- Mental health economic studies predominantly examine the affordability and value for money of individual programs [@RN34]. Yet single purpose models that assume static systems may be inadequate for the decision support needs of policymakers and service planners [@PC2020; @Occhipinti2021].  -->

### 2022-07-25 Markdown/Manuscript/Child_RMDs/MS_Results.Rmd
fiddling

```{r child="../Child_RMDs/XX_Funs.Rmd", echo=FALSE}
```
```{r child="../Child_RMDs/MS_Tables.Rmd", echo=FALSE}
```
```{r child="../Child_RMDs/MS_Figures.Rmd", echo=FALSE}
```
<!-- Add child RMDs for results content -->
```{r child="../Child_RMDs/MS_Imp_Guidelines.Rmd", echo=FALSE}
```
```{r child="../Child_RMDs/MS_Imp_Toolkit.Rmd", echo=FALSE}
```
```{r child="../Child_RMDs/MS_Imp_Example.Rmd", echo=FALSE}
```

>>>>

```{r child="../Child_RMDs/XX_Funs.Rmd", echo=FALSE}
```
```{r child="../Child_RMDs/MS_Tables.Rmd", echo=FALSE}
```
```{r child="../Child_RMDs/MS_Figures.Rmd", echo=FALSE}
```
<!-- Add child RMDs for results content -->

# Guidelines
```{r child="../Child_RMDs/MS_Imp_Guidelines.Rmd", echo=FALSE}
```

# Framework
```{r child="../Child_RMDs/MS_Imp_Toolkit.Rmd", echo=FALSE}
```

# Application
```{r child="../Child_RMDs/MS_Imp_Example.Rmd", echo=FALSE}
```
